The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-12-08 outputs/docs/events/paper.Rmd
Get speaker splitter working
Add counts of sitting days

elections <-
  read_csv("../../../inputs/misc/misc_elections_data.csv", col_types = cols())

governments <-
  read_csv("../../../inputs/misc/change_of_pm.csv", col_types = cols())

@@

In order to effectively categorise the topics of the entire Hansard, we chose to use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts. In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.

@@

@@

In terms of other issues, in the Senate, the PDF for 10 August 1917 may be the wrong one. It says that it is for 10 January 1918 on the cover sheet, but there's no an entry for 10 January 1918. Similarly for 1918-12-18 and 1917-08-01.

@@

elections %>% 
  filter(election == 1) %>% 
  select(year, electionDate, electionWinner) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 8)

@@

governments %>%
  kable(booktabs = T, caption = "Change in prime ministers") %>%
  kable_styling(font_size = 8)

>>>>

elections <-
  read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())

governments <-
  read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols())

@@

In order to effectively categorise the topics of the entire Hansard, we chose to use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts. In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent. One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time. A multinomial approach would not have this property.

@@

**[Add graph of example.]**

@@

In terms of other known issues, in the Senate, the PDF for the website date 10 August 1917 may be wrong. When downloaded the PDF says that it is for 10 January 1918 on the cover sheet, but there's no website entry for 10 January 1918. This is also the case for 18 December 1918 (which contains the PDF for 28 November 1918), and for 1 August 1917 (which contains the PDF for 10 August 1917).

@@

elections %>% 
  filter(election == 1) %>% 
  select(-election, -comment) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 8)

@@

governments %>%
  rename(
    "Government" = "government",
    "Prime Minister" = "primeMinister",
    "Party" = "party",
    "Start" = "start",
    "End" = "end",
    "Died in Office" = "diedInOffice",
    "HoR" = "hor",
    "Senate" = "senate"
    ) %>% 
  kable(booktabs = T, caption = "Change in prime ministers") %>%
  kable_styling(font_size = 8) %>% 
  footnote(general = "Here is a general comments of the table. ",
           number = c("Footnote 1; ", "Footnote 2; "),
           alphabet = c("Footnote A; ", "Footnote B; "),
           symbol = c("Footnote Symbol 1; ", "Footnote Symbol 2")
           )
